Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-16 papers/B1555_EdgeOn/B1555_letter.tex
Update mass term in Table 2 due to redshift change
Text change in Discussion

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$141.3$ &	$95.05$	  \\
$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$81.36$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\hline
\end{tabular}

@@

We present new lens models of B1555+375. With the new imaging from SHARP $K^{\prime}$ band, the most significant difference comparing to previous modelling is a new edge-on disk component. With a bulge plus an edge-on disk, our models fairly match to the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail. Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}. Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375. An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues. This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations. It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in the strongly lensed system.

@@

Given the assumption that lens galaxy has smooth gravitational potential, only substructure perturbations can cause flux ratio anomalies (in ideal case, i.e. no dust extinction, micro lensing, scattering etc.). Numerical simulations demostrate this idea with known flux anomalous lensed quasars. In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalies. By adding subhaloes on to those systems, only one out of six lens systems reproduce the flux anomalies. The rest of them are unlikely to have substructure originated flux anomalies, including our target B1555+375. \citet{Xu14} conclude the failure on B1555+375 due to improper lens models. This result supports our discovery in both observation and lens modelling, that an edge-on disk lies  between the radio merging double explain its flux ratio anomaly.

From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g. include an exponential disk), rather than just assuming smooth potential. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. It is important to fully consider non-substructure effects before any statistical analysis .Otherwise, possible ``false'' substructures detected by flux anomalies can serverly bias the data analysis. Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena and impacts on estimated mass and also other derived properties. We would like to draw attention to this non-substructure effect caused by a large, high ellipcity edge-on disk. For precise measurements on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects.

Our results also show that multi-wavelength imagimg is helpful to explore flux anomalous lensed quasars. Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With an high ellipcity edge-on disk, our new lens models adequately explain the flux ratio anomaly. Lack of knowledge of the lens galaxies can lead to improper lens modelling and bias to statistics among substructure detection. With the first system analyzing and showing that an edge-on disk from the lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. An edge-on disk structure may also able to expalin the flux ratio anomalies of these systems.\\

>>>>

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$141.3$ &	$144.6$	  \\
$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$123.8$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\hline
\end{tabular}

@@

We present new lens models of B1555+375. With the new imaging from SHARP $K^{\prime}$ band, the most significant difference comparing to previous modelling is a new edge-on disk component. With a bulge plus an edge-on disk, our models fairly match to the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail. Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}. Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375. An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues. This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations. It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in a strongly lensed system.

@@

Given the assumption that lens galaxy has smooth gravitational potential, only substructure perturbations can cause flux ratio anomalies (in ideal case, i.e. no dust extinction, micro lensing, scattering etc.). Numerical simulations demostrate this idea with known flux anomalous lensed quasars. In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalies. By adding subhaloes on to those systems, only one out of six lens systems reproduces the flux anomalies. The rest of them are unlikely to have substructure originated flux anomalies, including our target B1555+375. \citet{Xu14} conclude the failure on B1555+375 is due to improper lens models. This result supports our discovery in both observation and lens modelling, that an edge-on disk lies  between the radio merging double explain its flux ratio anomaly.

From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g. include an exponential disk), rather than just assuming smooth potential. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis. Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena. For precise measurements on substurcture population, mass function, and any derived properties from strongly lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects. We would like to draw attention to this edge-on disk orginated flux anomalies due to its impacts on substructure searching.

Our results also demostrate that multi-wavelength imaging is helpful to explore flux anomalous lensed quasars. Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With an high ellipcity edge-on disk, our new lens models adequately explain the flux ratio anomaly. Lack of knowledge of lens galaxies can lead to improper lens modelling and bias to statistics among substructure detections. With the first system analyzing and finding that an edge-on disk from the lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.\\
